Functional vs. Object Oriented Programming

### 2015-10-06 article.tex
Images with captions and pdf.

\documentclass{proc}

\usepackage{natbib}
\usepackage{url}

\begin{document}

@@

>>>>

\documentclass{article}

\usepackage{natbib}
\usepackage{url}
\usepackage{graphicx}

\graphicspath{ {img/} }
\begin{document}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{1}
\caption{The graph represents the distribution of both FP and OOP paradigm in different algorithms.}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{2}
\caption{The graph shows the distribution of the LOC of different languages implementation for different algorithms.}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{3}
\caption{The graph shows the LOC used to solve each algorithm for the same language.}
\end{figure}
